Lavaca Bay nutrient loading manuscript files

### 2023-10-12 README.Rmd
accepted version
add manuscript and snapshot

This repo contains the files used to generate:

Schramm, M. TBD. Linking watershed nutrient loading to estuary water quality with Generalized Additive Models.

>>>>

This repo contains the rmarkdown manuscript files used to generate the following accepted manuscript:

Schramm MP. 2023. Linking watershed nutrient loading to estuary water quality with generalized additive models. PeerJ 11:e16073 https://doi.org/10.7717/peerj.16073
